Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-10 draft.tex
good

For an open set $V$ the cochain map $I^{\partial}(V)$ admits the following explicit retract $r_\phi^\partial(V)$ defined on linear elements $x \otimes \alpha$ in $\Sym (\fg \otimes \Omega^\bu_c(V)[1])$ by the formula
\[
r_{\phi}^\partial (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t) \pm \d_{\rm CE} (x \otimes \pi^* \alpha \phi ) .
\]
The map $r_\phi^\partial (V)$ is extended to the entire symmetric algebra in the obvious way.

>>>>

For an open set $V$ the cochain map $I^{\partial}(V)$ admits an explicit retract $r_\phi^\partial(V)$ defined on linear elements $x \otimes \alpha$ in $\Sym (\fg \otimes \Omega^\bu_c(V)[1])$ by the formula
\[
r_{\phi}^\partial (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t) \pm \d_{\rm CE} (x \otimes \pi^* \alpha \phi ) .
\]
The map $r_\phi^\partial (V)$ is extended to the entire symmetric algebra in the obvious way.
